---
###Final Project
###Name: JIAWEN ZHANG
###UMID: 67753497
##title: "Final Project"
##output: html_document
---
```{r}
library(dplyr)
library(ggplot2)
library(knitr)
library(moderndive)
library(skimr)
library(infer)
```

#temp: Mean temperature for the day in degrees Fahrenheit to tenths.

#max: Maximum temperature reported during the day in Fahrenheit to tenths--
#time of max temp report varies by country and region, so this will sometimes
#not be the max for the calendar day.

#min: Minimum temperature reported during the day in Fahrenheit to tenths--
#time of min temp report varies by country and region, so this will sometimes
#not be the min for the calendar day.

#stp: Mean station pressure for the day in millibars to tenths.
#slp: Mean sea level pressure for the day in millibars to tenths.
#dewp: Mean dew point for the day in degrees Fahrenheit to tenths.
#wdsp: Mean wind speed for the day in knots to tenths.
#prcp: Total precipitation (rain and/or melted snow) reported during the day in inches and hundredths;
#will usually not end with the midnight observation--i.e., may include latter part of previous day.
#.00 indicates no measurable precipitation (includes a trace).
#fog: Indicators (1 = yes, 0 = no/not reported) for the occurrence during the day

#knitr::opts_knit$set(root.dir = '~/Downloads/Discussion 05')

#Read the target file and browse the data.
```{r setup, include=FALSE}
getwd()
setwd("C:/Users/92437/Desktop/Operation_M/registered courses/Fall_2021/544/final project")
getwd()
weather_data <- read.csv("training_data_with_weather_info_week_1.csv")
glimpse(weather_data)
```

#Switch the data tyoe of th <Date> with <Date> tyep. And Order the month in month order.
```{r cars}
weather_data$Date <- as.Date(weather_data$Date,"%m/%d/%y")
weather_data$month <- factor(weather_data$Month,levels = c("January","February","March"))
#weather_data$Month <- as.Date(weather_data$Month,"%B")
glimpse(weather_data)
```

#Filter the whole weather dataset to find all the data associated with New York State and Michigan State
```{r pressure, echo=FALSE}
#Find specific data associated with New York State
all_NYS_data <- weather_data %>%
  filter(Province.State == "New York")

View(all_NYS_data)
```

```{r}
#Find specific data associated with Michigan State
all_MIS_data <- weather_data %>%
  filter(Province.State == "Michigan")

View(all_MIS_data)
```


#Use line grah
```{r}
#line graph for wind speed of New York State in January
NYS_wind_Jan <- all_NYS_data %>%
  filter(Month == "January") %>%
  select(Date,wdsp)

ggplot(NYS_wind_Jan,aes(x=Date,y=wdsp))+
  geom_line(alpha=0.6)+
  geom_point(alpha=0.5,size=0.9)+
  ylim(0,15)
```

```{r}
#line graph for wind speed of Michigan State in January
MIS_wind_Jan <- all_MIS_data %>%
  filter(Month == "January") %>%
  select(Date,wdsp)

ggplot(MIS_wind_Jan,aes(x=Date,y=wdsp))+
  geom_line(alpha=0.6)+
  geom_point(alpha=0.5,size=0.9)+
  ylim(0,15)
```


```{r}
#The data about the precipitation in New York State
NYS_prec <- all_NYS_data %>%
  select(month, prcp)

NYS_prec_summary <- NYS_prec %>%
  filter(month != "")%>%
  group_by(month) %>%
  summarise(prec_mean = mean(prcp, na.rm = TRUE),
            prec_sd = sd(prcp, na.rm =TRUE),
            daily_max_prec = max(prcp),
            daily_min_prec = min(prcp),
            first_quantile = quantile(prcp, 0.25, na.rm=TRUE),
            second_quantile = quantile(prcp, 0.5, na.rm=TRUE),
            third_quantile = quantile(prcp, 0.75, na.rm=TRUE)
            )
```

```{r}
#The data about the precipitation in michigan State
MIS_prec <- all_MIS_data %>%
  select(month, prcp)

MIS_prec_summary <- MIS_prec %>%
  filter(month != "")%>%
  group_by(month) %>%
  summarise(prec_mean = mean(prcp, na.rm = TRUE),
            prec_sd = sd(prcp, na.rm =TRUE),
            daily_max_prec = max(prcp),
            daily_min_prec = min(prcp),
            first_quantile = quantile(prcp, 0.25, na.rm=TRUE),
            second_quantile = quantile(prcp, 0.5, na.rm=TRUE),
            third_quantile = quantile(prcp, 0.75, na.rm=TRUE)
            )
```


#Explore all the data associated with the temperature, whatever maximum temperature, minimum temperature,mean temperature and maximum temperature in each month in New York State and Michigan State.
```{r}
#Explore the data about temperatures in New York State, and show all the data in the form of box-plot
NYS_temp_data <- all_NYS_data %>%
  summarise(month = Month,
            date = Date,
            max_temp = max,
            min_temp = min,
            mean_temp = temp
            ) %>%
  mutate(max_temp_changes = max_temp - min_temp)

ggplot(NYS_temp_data,aes(x=factor(month),y=mean_temp))+
  geom_boxplot()
```

```{r}
#Explore the data about temperatures in Michigan State, and show all the data in the form of box-plot
MIS_temp_data <- all_MIS_data %>%
  summarise(month = Month,
            date = Date,
            max_temp = max,
            min_temp = min,
            mean_temp = temp
            ) %>%
  mutate(max_temp_changes = max_temp - min_temp)

ggplot(MIS_temp_data,aes(x=factor(month),y=mean_temp))+
  geom_boxplot()
```

#Use filter() function to find the temperature data of New York State in February.
```{r}
#visualize the February temperature changes in New York State and Michigan State with line graphs
NYS_temp_data_Feb <- NYS_temp_data %>%
  filter(month == "February")

ggplot(NYS_temp_data_Feb,aes(x=date,y=mean_temp))+
  geom_line(size=1.5,alpha=0.5)
```

#Explore the relation between timeline and temperature, and use linear model to visualize the relationship
```{r}
#visualize the temperature changes in New York State and Michigan State by day, and model the linear relationship
ggplot(NYS_temp_data,aes(x=date,y=mean_temp))+
  geom_point(alpha=0.2,size=2)+
  xlab("timeline")+
  ylab("temperature")+
  geom_smooth(method = "lm", se = FALSE)
```

#Select 20 days from Febuaryu as samples to be sampling distribution for both New York State and Michigan State
```{r}
#Explore the regression models of the factors in New York State and Michigan State in February
NYS_sample <- all_NYS_data %>%
  filter(month == "February") %>%
  sample_n(size = 20)

NYS_sample %>% skim()
```

```{r}
MIS_sample <- all_MIS_data %>%
  filter(month == "February") %>%
  sample_n(size = 20)

MIS_sample %>% skim()
```


```{r}
##Explore the relationship between dew point and wind speed in New York State and Michigan State with simple linear models
NYS_sample %>%
  get_correlation(formula = dewp ~ wdsp)

ggplot(NYS_sample,aes(x = dewp, y = wdsp)) +
  geom_point(alpha=0.2,size=2) +
  labs(x = "Dew Point",
       y = "Wind Speed",
       title = "Relationship between dew point and wind speed") +
  geom_smooth(method = "lm", se = FALSE,color = "red")

NYS_model <- lm(dewp ~ wdsp,data = NYS_sample)

get_regression_table(NYS_model)
```

```{r}
MIS_sample %>%
  get_correlation(formula = dewp ~ wdsp)

ggplot(MIS_sample,aes(x = dewp, y = wdsp)) +
  geom_point(alpha=0.3,size=2) +
  labs(x = "Dew Point",
       y = "Wind Speed",
       title = "Relationship between dew point and wind speed") +
  geom_smooth(method = "lm", se = FALSE,color = "red")

MIS_model <- lm(dewp ~ wdsp,data = MIS_sample)

get_regression_table(MIS_model)
```

```{r}
##Explore the relationship among station pressure, sea level pressure and fog in New York State in February
NYS_sample %>% 
  select(stp,slp,fog) %>%
  skim()

NYS_sample %>%
  get_correlation(formula = stp ~ slp)
```

```{r}
ggplot(NYS_sample,aes(x=stp, y=slp, color=factor(fog))) +
  geom_point(alpha=0.25,size = 2.5) +
  labs(x = "average station pressure",
       y = "average sea level pressure",
       color= "fog or not fog",
       title = "Relationship between station pressure, sea level pressure and fog conditions")+
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
NYS_model3 <- lm(stp ~ slp * fog, data = NYS_sample)
get_regression_table(NYS_model3)
```

```{r}
NYS_MIS_Feb_info <- weather_data %>%
  filter((Province.State == "Michigan" | Province.State == "New York") & Month == "February")
glimpse(NYS_MIS_Feb_info)

obs_diff_prop <- NYS_MIS_Feb_info %>%
  specify(stp ~ Province.State) %>%
  calculate(stat = "diff in means", order = c("New York","Michigan"))
print(obs_diff_prop)


null_distribution <- NYS_MIS_Feb_info %>%
  specify(formula = stp ~ Province.State) %>%
  hypothesise(null = "independence") %>%
  generate(reps = 1000,type ="permute") %>%
  calculate(stat = "diff in means", order = c("New York", "Michigan")) 

head(null_distribution)

visualize(null_distribution, bins = 6) + 
  shade_p_value(obs_stat = obs_diff_prop, direction = "right")


set.seed(200)
null_distribution %>% 
  get_p_value(obs_stat = obs_diff_prop, direction = "right")
##if p-value is larger than 0.05, so we will not reject the null hypothesis.
```

